---
title: "Build & publish website with `workflowr` functions"
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 


- TODO

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Use `workflowr` R function `wflow_build` to render Rmd files and build your website.  
- Use `workflowr` R function `wflow_publish` to 
- Use `workflowr` R function `wflow_status` to 


::::::::::::::::::::::::::::::::::::::::::::::::

```{r, eval = FALSE}
wflow_status()
```


```{r, eval = FALSE}
# from within the 'root' directory of your new project
wflow_build(".")
```




```{r, eval = FALSE}
wflow_status()
```

:::::::::::::::::::::::::::::::::::::: challenge

### How does the output of `wflow_status` change after adding a new Rmd file to the "analysis" subdirectory? 


First, look at the output of `wflow_status`. Run it again if you lost its output.  
Then, create a new Rmd file called "preliminary-statistical-modeling.Rmd" and save it in your analysis subdirectory.  
Run `wflow_status` again and compare the new output with the current output.







:::::::::::::: solution

### `wflow_status()` output before adding preliminary-statistical-modeling.Rmd:

```
Status of 3 Rmd files

Totals:
 3 Unpublished

The following Rmd files require attention:

Unp analysis/about.Rmd
Unp analysis/index.Rmd
Unp analysis/license.Rmd

Key: Unp = Unpublished

The current Git status is: working directory clean

To publish your changes as part of your website, use `wflow_publish()`.
To commit your changes without publishing them yet, use
`wflow_git_commit()`.
```



### `wflow_status()` after adding preliminary-statistical-modeling.Rmd to analysis subdirectory:

```
Status of 3 Rmd files

Totals:
 3 Unpublished

The following Rmd files require attention:

Unp analysis/about.Rmd
Unp analysis/index.Rmd
Unp analysis/license.Rmd

Key: Unp = Unpublished

The current Git status is: working directory clean

To publish your changes as part of your website, use `wflow_publish()`.
To commit your changes without publishing them yet, use
`wflow_git_commit()`.
> wflow_status()
Status of 4 Rmd files

Totals:
 3 Unpublished
 1 Scratch

The following Rmd files require attention:

Unp analysis/about.Rmd
Unp analysis/index.Rmd
Unp analysis/license.Rmd
Scr analysis/preliminary-statistical-modeling.Rmd

Key: Unp = Unpublished, Scr = Scratch (Untracked)

The current Git status is:

    status substatus                                          file
 untracked untracked analysis/preliminary-statistical-modeling.Rmd

To publish your changes as part of your website, use `wflow_publish()`.
To commit your changes without publishing them yet, use
`wflow_git_commit()`.
```






:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::




