---
title: "Build & publish website with `workflowr` functions"
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 


- TODO

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Use `workflowr` R function `wflow_build` to render Rmd files and build your website.  
- Use `workflowr` R function `wflow_publish` to 
- Use `workflowr` R function `wflow_status` to 


::::::::::::::::::::::::::::::::::::::::::::::::

```{r, eval = FALSE}
wflow_status()
```


```{r, eval = FALSE}
# from within the 'root' directory of your new project
wflow_build(".")
```




```{r, eval = FALSE}
wflow_status()
```

:::::::::::::::::::::::::::::::::::::: challenge

### How does the output of `wflow_status` change after adding a new Rmd file to the "analysis" subdirectory? 


First, look at the output of `wflow_status`. Run it again if you lost its output.  
Then, create a new Rmd file called "preliminary-statistical-modeling.Rmd" and save it in your analysis subdirectory.  
Run `wflow_status` again and compare the new output with the current output.







:::::::::::::: solution

### `wflow_status()` output before adding preliminary-statistical-modeling.Rmd:

```

```



### `wflow_status()` after adding preliminary-statistical-modeling.Rmd to analysis subdirectory:

```

```






:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::




