---
title: "Setting up a new project with `workflowr`"
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 


- TODO

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Use R to install `workflowr` R package on your computer.    
- Use `workflowr` functions in an R session to set up a new project.  


::::::::::::::::::::::::::::::::::::::::::::::::


```{r, install-pkg, eval = FALSE}
install.packages("workflowr")
```


```{r, eval= FALSE}
library(workflowr)
wflow_start("~/Desktop/try-workflow1")
```





:::::::::::::::::::::::::::::::::::::: challenge

### What is the directory structure of my new project? 

Where is the file called `about.Rmd`? 

:::::::::::::: solution

### Looking at the directory structure of my project

**At a terminal prompt**, type:

```
ls -R myproject
```

after replacing "myproject" with the name of your new project.

**Within an R session**, type: 

```{r, eval = FALSE}
list.files(recursive = TRUE, no.. = TRUE)
```

when you're in the new project (root) directory. 


```
myproject/
├── .gitignore
├── .Rprofile
├── _workflowr.yml
├── analysis/
│   ├── about.Rmd
│   ├── index.Rmd
│   ├── license.Rmd
│   └── _site.yml
├── code/
│   ├── README.md
├── data/
│   └── README.md
├── docs/
├── myproject.Rproj
├── output/
│   └── README.md
└── README.md
```

We see that `about.Rmd` is in the directory `myproject/analysis/`.




:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::


The two required subdirectories are analysis/ and docs/. These directories should never be removed from the workflowr project.

analysis/: This directory contains all the source R Markdown files for implementing the data analyses for your project. It also contains a special R Markdown file, index.Rmd, that does not contain any R code, but will be used to generate index.html, the homepage for your website. In addition, this directory contains the important configuration file _site.yml, which you can use to edit the theme, navigation bar, and other website aesthetics (for more details see the documentation on R Markdown websites). Do not delete index.Rmd or _site.yml.


docs/: This directory contains all the HTML files for your website. The HTML files are built from the R Markdown files in analysis/. Furthermore, any figures created by the R Markdown files are saved here. Each of these figures is saved according to the following pattern: docs/figure/<insert Rmd filename>/<insert chunk name>-#.png, where # corresponds to which of the plots the chunk generated (since one chunk can produce an arbitrary number of plots)3.


The workflowr-specific configuration file is **_workflowr.yml**. It will apply the workflowr reproducibility checks consistently across all your R Markdown files. The most critical setting is knit_root_dir, which determines the directory where the files in analysis/ will be executed. The default is to execute the code in the root of the project where _workflowr.yml is located (i.e. "."). To instead execute the code from analysis/, change the setting to knit_root_dir: "analysis". See ?wflow_html for more details.

*Also required is the RStudio project file*, in this example myproject.Rproj. **Even if you are not using RStudio, do not delete this file** because the workflowr functions rely on it to determine the root directory of the project.


* `data/`: This directory is for raw data files.

* `code/`: This directory is for code that might not be appropriate to include
in R Markdown format (e.g. for pre-processing the data, or for long-running
code).

* `output/`: This directory is for processed data files and other
outputs generated from the code and data. For example, scripts in
`code/` that pre-process raw data files from `data/` should save the
processed data files in `output/`.

The `.Rprofile` file is a regular R script that is run once when the project is
opened. It contains the call `library("workflowr")`, ensuring that workflowr is
loaded automatically each time a workflowr-project is opened.


:::::::::::::::::::::::::::::::::::::: challenge

### How do I create a new Rmd file for use in my data analysis?   

Using either R or shell commands, create a new Rmd file called "exploratory-data-analysis.Rmd" and save it in your "analysis" subdirectory. 

:::::::::::::: solution

### Creating "exploratory-data-analysis.Rmd"

**In Rstudio**: 
- File menu > New File > Rmarkdown...   
- Fill in prompts for document title, date, etc.   
- File menu > Save as... > Navigate to "analysis" subdirectory, then click "Save".

**With a text editor (like `vim`)**:

- Create a new file by typing at the prompt: `vim analysis/exploratory-data-analysis.Rmd`; be sure to use the correct relative file path  
- Insert needed yaml at top of the new text file.   
- Save file. 





:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::






